SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 results.tex
Analysis of xalancbmk and cactuBSSN

PPF yields a geometric mean speedup of \textbf{26.95\%} over the baseline. 
This is equivalent to \textbf{4.63\%} over DA-AMPM, \textbf{4.61\%} over BOP 
and \textbf{3.78\%} over SPP. Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints. PPF fails to match the improvement offered by BOP only for 
{\tt 607.cactuBSSN\_s} and {\tt 654.roms\_s} traces.

>>>>

PPF yields a geometric mean speedup of \textbf{26.95\%} over the baseline. 
This is equivalent to \textbf{4.63\%} over DA-AMPM, \textbf{4.61\%} over BOP 
and \textbf{3.78\%} over SPP. Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints. 
An interesting case to see here is {\tt 623.xalancbmk}. Despite SPP 
underperforming on that application, PPF manages to considerably outperform 
the next best prefetcher -- BOP. Since this benchmark has varying prefetch 
deltas, SPP's conservative throttling mechanism catches that and quickly halts 
prefetching at an average depth of 2.1. On the other hand, PPF's more efficient 
accuracy check enables it to prefetch upto a lookahead depth of 3.3. Doing this, PPF 
suggests 1.61 times more total prefetches and 2.53 times more 
useful prefetches than SPP.

The only benchmark where PPF fails to match the improvement offered by other prefetchers 
is {\tt 607.cactuBSSN\_s}. \newline Based on our observation of prefetching behavior, we gather that
BOP's aggressive and localised nature can tackle this workload really well; as opposed
to SPPs lookahead nature. As a result, SPP, and hence PPF, underperform on this benchmark.
